Paper Visualization

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made important changes

# Display the list of top 15 influential authors
print(top_influential_authors)
```

@@

@@

```{r How Many Topics}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  influential_dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014", "CaoJuan2009", "Arun2010"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 200),  # Fewer iterations for quicker results
  mc.cores = 2L,
  verbose = TRUE
)

@@

@@

tab_df(best_matches)
```

@@

>>>>

# Display the list of top 15 influential authors
print(top_influential_authors)

output_file_path <- file.path(output_directory, "images and tables", "influential_authors_descriptive_statistics.html")

tab_df(top_influential_authors,
  file = output_file_path)
```

@@

# Add key event annotations
key_events <- data.frame(
  date = as.Date(c("1982-05-11", "1983-09-30", "1984-04-23", "1984-10-01", 
                   "1985-03-02", "1985-07-25", "1985-10-02", "1986-02-01", 
                   "1986-08-14")),  # Add the key event dates
  event = c("Term 'AIDS' Introduced", "CDC AIDS Guidelines", "HHS HIV/AIDS", 
            "First HIV Blood Test", "First HIV Test Approved", "Rock Hudson's Diagnosis", 
            "HIV Transmission Routes", "'HIV' Renamed", "AZT Approved"),  # Shorter descriptions
  y = c(-25, -25, -25, -25, -25, -25, -25, -25, -25)  # Set y position for text labels
)

# Adding the annotations to the plot
time_series_plot <- time_series_plot +
  geom_vline(data = key_events, aes(xintercept = date), linetype = "dashed", alpha = 0.5) +  # Vertical dashed lines
  geom_text(data = key_events, aes(x = date, y = y, label = event), 
            size = 3, angle = 90, vjust = -0.5, hjust = 0, inherit.aes = FALSE)  # Event labels

@@

```{r How Many Topics, eval=FALSE, include=FALSE}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  influential_dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014", "CaoJuan2009", "Arun2010"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 200),  # Fewer iterations for quicker results
  mc.cores = 2L,
  verbose = TRUE
)

@@

Six Topics!

@@

output_file_path <- file.path(output_directory, "images and tables", "topic_matches_table.html")

tab_df(best_matches, ,
  file = output_file_path)
```

@@

```{r Topic Prevelance over Time Plot}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(scales)
library(topicmodels)

# Function to get topic distributions for a set of documents
get_topic_distribution <- function(lda_model, dtm) {
  topic_dist <- posterior(lda_model)$topics
  colnames(topic_dist) <- paste0("Topic_", 1:ncol(topic_dist))
  cbind(data.frame(Document = rownames(dtm)), as.data.frame(topic_dist))
}

# Get topic distributions for all documents and influential authors' documents
all_topic_dist <- get_topic_distribution(lda_model, dtm)
influential_topic_dist <- get_topic_distribution(influential_lda, influential_dtm)

# Add date and author information
all_topic_dist$Date <- filtered_comments$Date[match(all_topic_dist$Document, rownames(dtm))]
all_topic_dist$Influential <- FALSE

influential_topic_dist$Date <- top_authors_comments$Date[match(influential_topic_dist$Document, rownames(influential_dtm))]
influential_topic_dist$Influential <- TRUE

# Combine datasets
combined_topic_dist <- rbind(all_topic_dist, influential_topic_dist)

# Calculate monthly topic prevalence
monthly_topic_prevalence <- combined_topic_dist %>%
  mutate(Month = floor_date(Date, "month")) %>%
  group_by(Month, Influential) %>%
  summarise(across(starts_with("Topic_"), mean)) %>%
  pivot_longer(cols = starts_with("Topic_"), names_to = "Topic", values_to = "Prevalence")

# Create a custom labeler for facet labels
facet_labels <- c(`FALSE` = "All Authors", `TRUE` = "Influential Authors")

# Create the line plot for topic prevalence over time with better scaling
line_plot <- ggplot(monthly_topic_prevalence, aes(x = Month, y = Prevalence, color = Topic, group = Topic)) +
  geom_line(size = 1.5) +  # Increase line size for better visibility
  facet_wrap(~Influential, scales = "free_y", ncol = 1, labeller = labeller(Influential = facet_labels)) +  # Use labeller to rename facets
  scale_color_brewer(palette = "Dark2") +  # Use a palette with more distinct colors
  labs(title = "Topic Prevalence Over Time: Influential Authors vs Overall Discussion",
       x = "Date",
       y = "Topic Prevalence",
       color = "Topic") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)) +  # Rotate x-axis labels for better readability
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0.155, 0.1825))  # Zoom in on relevant y-axis range

# Print the plot
print(line_plot)

# Save the plot with a higher DPI for better clarity
output_file_path <- file.path(output_directory, "images and tables", "topic_prevalence_line_plot.png")
ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
```
